Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-27 docs/paper.tex
Worked on motivation of experiments

	\section{Experimental Results}
	\label{experiments}
	To compare the algorithms and variants described above with each other and with alternative MAPFM algorithms, two types of experiments were performed. In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM \cite{donszelmann2021,baauw2021,jong2021,bruin2021}. This comparison data originates in \cite{donszelmann2021}. The values compared are the fraction of instances solved, and the average run time per instance. It should be noticed that in the latter, the recorded run times converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), the fraction of instances solved is guiding in the analysis of results.
	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
			\caption{25\% wall, one team}
			\label{fig:i-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
			\caption{25\% wall, three teams}
			\label{fig:i-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
			\caption{75\% wall, one team}
			\label{fig:i-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
			\caption{75\% wall, three teams}
			\label{fig:i-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 50 maps by different ICTS-based algorithms}
		\label{fig:i-probs}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
			\caption{25\% wall, one team}
			\label{fig:r-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
			\caption{25\% wall, three teams}
			\label{fig:r-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
			\caption{75\% wall, one team}
			\label{fig:r-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
			\caption{75\% wall, three teams}
			\label{fig:r-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 200 maps by MAPFM algorithms}
		\label{fig:r-probs}
	\end{figure*}

	\restoregeometry
	\subsection{Experimental setup}
	Because MAPFM lies on the fringe of pathfinding research, no standard benchmark exists. For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was already a challenge computationally. This observation informed the creation of a map generator by the author of \cite{jong2021} with various parameters. Using this map generator, two types of 20x20 grids were generated:
	\begin{enumerate}
		\item 25\% wall: a grid with 25\% of tiles being obstacles.
		\item 75\% wall: a grid with 75\% of tiles being obstacles. 
	\end{enumerate}
	For each of these types, maps were generated with between $1$ and $25$ agents either all in the same team or partitioned into three teams as evenly as possible. When solving the instances, for each combination of map-type and number of teams, the number of agents was increased until 0\% of instances could be solved within a timeout of 120s, at which point no more data was recorded for greater numbers of agents.

>>>>

	\section{Experimental Results}
	\label{experiments}
	To compare the algorithms and variants described above with each other and with alternative MAPFM algorithms, two types of experiments were performed. In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM \cite{donszelmann2021,baauw2021,jong2021,bruin2021}. The data for the second experiment originates in \cite{donszelmann2021}.  In both experiments, there are three variables: the number of agents, the fraction of blocked grid tiles and the number of teams. The values measured are the fraction of instances solved and the average run time per instance. In the latter, the recorded run times converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), only the fraction of instances solved is used in the analysis of results.
	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
			\caption{25\% wall, one team}
			\label{fig:i-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
			\caption{25\% wall, three teams}
			\label{fig:i-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
			\caption{75\% wall, one team}
			\label{fig:i-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
			\caption{75\% wall, three teams}
			\label{fig:i-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 50 maps by different ICTS-based algorithms}
		\label{fig:i-probs}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
			\caption{25\% wall, one team}
			\label{fig:r-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
			\caption{25\% wall, three teams}
			\label{fig:r-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
			\caption{75\% wall, one team}
			\label{fig:r-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
			\caption{75\% wall, three teams}
			\label{fig:r-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 200 maps by MAPFM algorithms}
		\label{fig:r-probs}
	\end{figure*}

	\restoregeometry
	\subsection{Experimental setup}
	Because MAPFM lies on the fringe of pathfinding research, no standard benchmark exists. For MAPF, the Moving AI benchmarks \cite{sturtevant2012} are often used and potentially a new MAPFM standard benchmark could be defined by generating suitable team-partitions of agents for these MAPF instances; however, it was noticed that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was already a challenge computationally. This observation informed the creation of a map generator by the author of \cite{jong2021} with various parameters.

	%Using this generator, MAPFM instances situated on 20x20 grids with obstacles were generated by varying three variables: the number of agents; the fraction of blocked grid tiles; the number of teams.

	Using this map generator, two types of 20x20 grids similar to the random maps in \cite{sturtevant2012} were generated:

	\begin{enumerate}
		\item 25\% wall: a grid with 25\% of tiles being obstacles.
		\item 75\% wall: a grid with 75\% of tiles being obstacles. 
	\end{enumerate}
	For each of these types, maps were generated with between $1$ and $25$ agents either all in the same team or partitioned into three teams as evenly as possible. When solving the instances, for each combination of map-type and number of teams, the number of agents was increased until 0\% of instances could be solved within a timeout of 120s, at which point no more data was recorded for greater numbers of agents. This approach is similar to the method described in \cite{stern2019}.

	%In varying the number of obstacles and the number of agents, this setup is similar to those used in the MAPF literature \cite{stern2019}.

	% In varying the number of obstacles and the number of agents, the comparison is similar to those used in the MAPF literature \cite{stern2019}.

	%The purpose of

	%Although the maps with one team are equivalent to anonymous MAPF instances

	%While progressively increasing the number of agents is common in MAPF benchmarks
